Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-30 papers/contact/paper.tex
fixed percentages that Gross was wrong by, at end Tests skipped!

Although these recent works have introduced approximate functionals
for the contact value of the correlation
function\cite{yu2002fmt-dft-inhomogeneous-associating,
  gross2009density}, there has not been a study that specifically
addresses this contact value for an inhomogeneous hard-sphere fluid.
%
In this paper we introduce two definitions for the locally averaged
correlation function of an inhomogeneous system.
%
%% The first is more symmetric (which we call the $S$ case), while the
%% second involves a sphere-centered, assymetrical interpretation (the
%% $A$ case).
%
Given these definitions, we will present a thermodynamic derivation
for each correlation function from the free energy functional.  We
will then discuss the correlation functions of Yu and Wu and of Gross, and
will end by comparing all four approximations with Monte-Carlo
simulations of the hard-sphere fluid at a variety of hard-wall
surfaces.

@@

The asymmetric version of the correlation function once again displays
relatively smooth behavior with a few small
oscillations near the interface, and a somewhat elevated value within
a diameter of the hard surface, with the magnitude of this elevation
somewhat different in each configuration.  As was the case at low
density, our correlation function $g_\sigma^A$ matches very closely
the Monte Carlo data, reproducing quite well the structure near the
interface in each configuration, although in the spherical cavity
(Figure~\ref{fig:outer-40}), there is a small, but significant
discrepancy, comparable to the discrepancy found in the density
itself.  In each case, the correlation of Gross dramatically
underestimates the correlation at the interface, at one extreme by
\fixme{40\%} in the case of the spherical cavity
(Figure~\ref{fig:outer-40}), and at the other extreme by \fixme{10\%}
in the test-particle scenario (Figure~\ref{fig:inner-4-40}).

@@

We will show here the derivation of the $\beta\frac{\delta n_3^{A}(\mathbf{r}')}{\delta \sigma(\mathbf{r})/2}$, etc., terms for the assymetric case.  The derivation of the S correlation follows the same format using the symmetric conceptual approach introduced in \ref{sec:g-S} and the $\frac{\delta A_{HS}}{\delta n(\mathbf{r}')}$, etc., terms are straightforward (if tedious) derivatives.

>>>>

Although these recent works have introduced approximate functionals
for the contact value of the correlation
function\cite{yu2002fmt-dft-inhomogeneous-associating,
  gross2009density}, there has not been a study that specifically
addresses this contact value for an inhomogeneous hard-sphere fluid.
%
In this paper we introduce two definitions for the locally averaged
correlation function of an inhomogeneous system.
%
%% The first is more symmetric (which we call the $S$ case), while the
%% second involves a sphere-centered, asymmetrical interpretation (the
%% $A$ case).
%
Given these definitions, we will present a thermodynamic derivation
for each correlation function from the free energy functional.  We
will then discuss the correlation functions of Yu and Wu and of Gross, and
will end by comparing all four approximations with Monte-Carlo
simulations of the hard-sphere fluid at a variety of hard-wall
surfaces.

@@

The asymmetric version of the correlation function once again displays
relatively smooth behavior with a few small
oscillations near the interface, and a somewhat elevated value within
a diameter of the hard surface, with the magnitude of this elevation
somewhat different in each configuration.  As was the case at low
density, our correlation function $g_\sigma^A$ matches very closely
the Monte Carlo data, reproducing quite well the structure near the
interface in each configuration, although in the spherical cavity
(Figure~\ref{fig:outer-40}), there is a small, but significant
discrepancy, comparable to the discrepancy found in the density
itself.  In each case, the correlation of Gross dramatically
underestimates the correlation at the interface, at one extreme by
40\% in the case of the spherical cavity
(Figure~\ref{fig:outer-40}), and at the other extreme by 15\%
in the test-particle scenario (Figure~\ref{fig:inner-4-40}).

@@

We will show here the derivation of the $\beta\frac{\delta n_3^{A}(\mathbf{r}')}{\delta \sigma(\mathbf{r})/2}$, etc., terms for the asymmetric case.  The derivation of the S correlation follows the same format using the symmetric conceptual approach introduced in \ref{sec:g-S} and the $\frac{\delta A_{HS}}{\delta n(\mathbf{r}')}$, etc., terms are straightforward (if tedious) derivatives.
